---
title: '  '
output:
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
classoption: landscape

header-includes:
- \usepackage{longtable}
- \usepackage{booktabs}
- \usepackage{fancyhdr}
- \usepackage{lastpage}
- \pagestyle{fancy}
- \usepackage{geometry}
- \geometry{top = 1in, right=0.5in, left=0.5in, bottom = 1in}

---

<!-- Fontsize  -->
<!-- Fontsize  -->

<!-- \tiny -->
\scriptsize
<!-- \footnotesize -->
<!-- \small -->
<!-- \normalsize -->
<!-- \large -->
<!-- \Large -->
<!-- \LARGE -->
<!-- \huge -->
<!-- \Huge  -->

    
<!--- Define Headers and Footers --->
\fancypagestyle{plain}{%
  \renewcommand{\headrulewidth}{0pt}%
  \fancyhf{}%
  \fancyfoot[C]{\footnotesize Page \thepage\, of\, \pageref*{LastPage}}
  \setlength\footskip{0pt}
}

\lhead{\footnotesize Asana BioSciences, LLC\newline ASN007-101}
\rhead{\footnotesize Page \thepage\, of\, \pageref*{LastPage}}
\lfoot{Draft}
\cfoot{}
\rfoot{\footnotesize Date: \today}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

```

```{r}
library(data.table)
library(XLConnect)
library(ggplot2)
library(haven)
library(kableExtra)
library(magrittr)
library(tables)


load("AE_SUM.RData")

ae_daily_freq_dt1 <- ae_daily_freq_dt[as.numeric(EXDOSE) <= 3]
ae_daily_freq_dt2 <- ae_daily_freq_dt[as.numeric(EXDOSE) > 3]

ppct <- function(x){
  paste0("(", sprintf("%.1f", x), ")")
} 

ae_table <- function(rel = "All", dose_freq = "ASN007 Once Weekly", 
                     data = ae_weekly_freq_de,
                     ae_type = "Emergent") {  
  temp <- data[REL == rel & GRADE != "All" & trimws(PREFERRED.TERM) != ""]
  ttl <- paste0("Number and Percent of Patients with Treatment ", 
              ae_type, " Adverse Events: ", dose_freq, "\\\\ (by Grade per Dose Level)")
 
  tabular(Multicolumn(SYSTEM.ORGAN.CLASS, "SOC\\\\", width = 11, texify = T)*
          Factor(PREFERRED.TERM, "Preferred Term") ~
           Factor(EXDOSE, dose_freq, levelnames = levels(EXDOSE), texify = T)* 
             Factor(GRADE, "Grade")*
              Paste(Heading("n")*n*Heading()*sum, ppct*Heading("(\\%)")*pct, justify="r")*
                 DropEmpty(), data=temp) %>%
  toKable(booktabs=T,
      options=list(tabular="longtable",
        toprule=paste0("\\caption{", ttl, "}\\\\\\toprule"),
          midrule="\\midrule\\\\[-1\\normalbaselineskip]\\endhead\\hline\\endfoot"))
}

ae_table1 <- function(dose_freq = "ASN007 Once Weekly",
                      data = ae_weekly_freq_dt) {
  temp <- data[trimws(PREFERRED.TERM) != ""]
  ttl <- paste0("Number and Percent of Patients with Treatment Emergent/Related Adverse Events: ", dose_freq)

  tabular(Multicolumn(SYSTEM.ORGAN.CLASS, "SOC\\\\", width=6)*
          Heading("Preferred Term")*Factor(PREFERRED.TERM) ~
           Heading()*Factor(EXDOSE)* 
            Heading()*Factor(REL)*
              GRADE*Paste(Heading("n")*n*Heading()*sum, 
                                           ppct*Heading("(\\%)")*pct, justify="r")*
                 DropEmpty(), data=temp) %>%
  toKable(booktabs=T,
      options=list(tabular="longtable",
        toprule=paste0("\\caption{", ttl, "}\\\\\\toprule"),
          midrule="\\midrule\\\\[-1\\normalbaselineskip]\\endhead\\hline\\endfoot")) 
  }


ae_weekly_freq_dt1 <- ae_weekly_freq_dt[as.numeric(EXDOSE) <= 3]
ae_weekly_freq_dt2 <- ae_weekly_freq_dt[as.numeric(EXDOSE) > 3]

```

```{r}
library(compiler)
ae_table <- cmpfun(ae_table)
ae_table1 <- cmpfun(ae_table1)

ae_table(rel = "All", dose_freq = "ASN007 Once Daily",
                     data = ae_daily_freq_dt1,
                     ae_type = "Emergent")

```

\newpage

```{r}

ae_table(rel = "All", dose_freq = "ASN007 Once Daily",
                     data = ae_daily_freq_dt2,
                     ae_type = "Emergent")

```
\newpage

```{r}
ae_table(rel = "Related", dose_freq = "ASN007 Once Daily",
                     data = ae_daily_freq_dt1,
                     ae_type = "- Related")

```
\newpage

```{r}
ae_table(rel = "Related", dose_freq = "ASN007 Once Daily",
                     data = ae_daily_freq_dt2,
                     ae_type = "- Related")


```
\newpage
```{r}
ae_table(rel = "All", dose_freq = "ASN007 Once Weekly",
                     data = ae_weekly_freq_dt1,
                     ae_type = "Emergent")

```
\newpage

```{r}
ae_table(rel = "All", dose_freq = "ASN007 Once Weekly",
                     data = ae_weekly_freq_dt2,
                     ae_type = "Emergent")

```
\newpage
```{r}
ae_table(rel = "Related", dose_freq = "ASN007 Once Weekly",
                     data = ae_weekly_freq_dt1,
                     ae_type = "- Related")

```
\newpage

```{r}

ae_table(rel = "Related", dose_freq = "ASN007 Once Weekly",
                     data = ae_weekly_freq_dt2,
                     ae_type = "- Related")

```

\newpage
```{r}
ae_table1(dose_freq = "ASN007 Daily and Weekly Combined\\\\ (by Grade – All Daily and Weekly Dose Levels)",                    data = ae_combo_freq_dt)

```
