---
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../R_Output")})

output:
   pdf_document:
     latex_engine: xelatex
classoption: landscape

header-includes:
- \usepackage{array}
- \usepackage{fancyhdr}
- \usepackage{lastpage}
- \usepackage{caption}
- \pagestyle{fancy}
- \usepackage{geometry}
- \geometry{top = 1in, left = 1in, right = 1in, bottom = 1in}
- \usepackage{longtable}
- \usepackage{pgfplotstable}
- \usepackage{booktabs}
- \usepackage{multicol}
- \usepackage{multirow}
- \usepackage{siunitx}
- \usepackage{makecell}
- \setlength{\headheight}{32pt}
- \sisetup{ 
    round-mode = places,  round-precision = 2
   }
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, results = "asis")

big_col <- function(data){
  if(is.character(data)){
    nc <- length(data)
    nr <- 1
  } 
  else {
       nc <- NCOL(data); 
       nr <- NROW(data)
  }     
  prefix <- rep(paste0("\\hspace{", 2*(0:(nc-1)), "ex}"), each = nr)
  final  <- structure(paste0(prefix, unlist(data)), dim = c(nr, nc))
  final  <- apply(final, 1, function(x) paste0(x, collapse = " \\\\ "))
  if(is.character(data)) paste0("\\makecell[lb]{", final, "}")
  else paste0("\\makecell[lt]{", final, "}")
}


```

```{r}

latex_setup()

all_ae_dt <- data.table(read_sas("../adam/adae.sas7bdat"))

all_ae_dt <- all_ae_dt[SAFFL=="Y"]
all_ae_dt[, AETERM := sub("&", "\\\\&", AETERM)]

all_ae_dt[, c("COMP", "DOSE", "UNIT", "FREQ") := as.list(strsplit(TRTA, split=" ")[[1]]), by=1:NROW(all_ae_dt) ]
all_ae_dt[, DOSE:= as.numeric(DOSE)]
all_ae_dt[, TRTA := paste0(FREQ, " / ", DOSE, " mg")]

setorder(all_ae_dt, AEBODSYS, AEDECOD, FREQ, DOSE, SUBJID, AESTDY)

ID <- unique(all_ae_dt$AEDECOD)
ID1 <- ID[1: floor(length(ID)*1/2)]
ID2 <- setdiff(ID, ID1)

sub_set <- function(id) {
#  id <- ID1
ae_dt <- all_ae_dt[AEDECOD %in% id]


ae_dt[, no := 1:.N, .(AEBODSYS, AEDECOD, FREQ, DOSE, SUBJID)][ no > 1, 
                                 `:=`(TRTA = " ", SUBJID = " ")]

ae_dt[, no := 1:.N, .(AEBODSYS, AEDECOD)][ no > 1, 
                                 `:=`(AEBODSYS = " ", AEDECOD = " ", AETERM = " ")]

ae_dt[, AEDUR:= AEENDY - AESTDY + 1]

ae_dt[, `:=`(AESTDTC = paste0(AESTDTC, " (", AESTDY, ")"),
             AEENDTC = ifelse(trimws(AEENDTC) == "", "Onging", paste0(AEENDTC, " (", AEENDY, ")")),
             AEDUR = ifelse(!is.na(AEDUR), paste0(AEDUR," Days"), "- ") 
             )]
#ae_dt[, PART:=ifelse(ANL01FL=="Y", "A", "B")]

ae_dt[, LINE := "  "]

terms   <- c("AEBODSYS", "AEDECOD", "LINE") 
times   <- c("AESTDTC", "AEENDTC",  "AEDUR", "LINE")
attrs   <- c("AEREL", "AETOXGR",  "AESER","LINE")
acnout  <- c("AEACN",  "AEACNOTH", "AEOUT", "LINE")
subjtrt <- c("AEACN",  "AEACNOTH", "AEOUT", "LINE")

ae_dt[, `:=`(TRTA = sub("ASN007 ", "", TRTA),
             AEBODSYS  = gsub("([[:alpha:]])(.+)", "\\U\\1\\L\\2", AEBODSYS, perl = TRUE),
             AEDECOD  = gsub("([[:alpha:]])(.+)", "\\U\\1\\L\\2", AEDECOD, perl = TRUE),
             AETERM  = gsub("([[:alpha:]])(.+)", "\\U\\1\\L\\2", AETERM, perl = TRUE),
             AEREL  = gsub("([[:alpha:]])(.+)", "\\U\\1\\L\\2", AEREL, perl = TRUE),
             AEACN  = gsub("([[:alpha:]])(.+)", "\\U\\1\\L\\2", AEACN, perl = TRUE),
             AEACNOTH  = gsub("([[:alpha:]])(.+)", "\\U\\1\\L\\2", substr(AEACNOTH, 1,20), perl = TRUE),
             AEOUT  = gsub("([[:alpha:]])(.+)", "\\U\\1\\L\\2", AEOUT, perl = TRUE)
)]

# vars <- c("AEREL","AESEV","AEACN","AEACNOTH","AEOUT")
# ae_dt[, (vars):= lapply(.SD, tools::toTitleCase), .SDcols= vars]

ae_dt <- data.table(
            terms  = big_col(ae_dt[, terms, with = F]),
            trtid  = big_col(ae_dt[, .(TRTA, SUBJID)]),
            times  = big_col(ae_dt[, times, with = F]),
            attrs  = big_col(ae_dt[, attrs, with = F]),
            acnout = big_col(ae_dt[, acnout, with = F])
            )

paste(apply(ae_dt, 1, function(x) paste(x, collapse = " & ")), collapse = " \\\\ ")

}

header <- data.table(
                  terms = big_col(c("System Organ Class", "Preferred Term")),
                  trtid = big_col(c("Treatment", "Subj ID")),
                  times = big_col(c("Start Date (Days)", "Stop Date (Days)", "Duration")),
                  attrs = big_col(c("Relatedness", "Grade", "Serious"))
                  ,
                 acnout = big_col(c("Action", "Other Action", "Outcome"))
                 )

                            
header <- paste(paste(header, collapse = " & "), collapse=" \\\\ ") 

body1 <- sub_set(ID1) 
body2 <- sub_set(ID2) 

```

\renewcommand{\tablename}{Listing}

\footnotesize
\clearpage


\begin{longtable}{p{3.6in}p{0.6in}p{1in}p{1in}p{1.8in}}
  \caption{Adverse Events Grouped by SOC and PT \\ (Safety Population)} \\
  \toprule   %thicker \hline
  `r header` \\
  \midrule \\[-1\normalbaselineskip] 
  \endhead
  \hline
  \\
  %\multicolumn{7}{l}{{$^1$ Continued on Next Page \ldots}} \\ %footnote after each page of table -->
  %\multicolumn{7}{l}{{$^2$ New line \ldots}} \\               %footnote after each page of table -->
  \endfoot 
  `r body1`  \\
  \hline
\end{longtable}

\begin{longtable}{p{3.6in}p{0.6in}p{1in}p{1in}p{1.8in}}
  \caption{Adverse Events Grouped by Subject \\ (Safety Population)} \\
  \toprule   %thicker \hline
  `r header` \\
  \midrule \\[-1\normalbaselineskip] 
  \endhead
  \hline
  \\
  %\multicolumn{7}{l}{{$^1$ Continued on Next Page \ldots}} \\ %footnote after each page of table -->
  %\multicolumn{7}{l}{{$^2$ New line \ldots}} \\               %footnote after each page of table -->
  \endfoot 
  `r body2`  \\
  \hline
\end{longtable}

